Bayesian determination of the effect of a deep eutectic solvent on the structure of lipid monolayers

### 2018-10-09 reports/preprint.tex
First set of edits/typos

The custom model for each lipid, based on the standard two-layer model widely used for lipids on water, was first fitted to the experimental XRR data, and the associated SLD profiles are shown in Figure \ref{fig:lipids}.
Table \ref{tab:liptab} presents the mean value, and asymmetric uncertainies that correspond to a \SI{95}{\percent} confidence interval, for the PDF for each of the varying parameters; the tail tile angle, $\theta_t$, the interfacial roughness, $\sigma$, the head and tail volumes, $V_h$ and $V_t$ respectively, and the head layer thickness, $d_h$.
In order to constrain the fitting process only $\theta_t$ and $\sigma$ were allowed to vary independently of surface pressure. The other parameters, $V_h$, $V_t$ and $d_h$ were fitted to a single value for all of the surface pressures measured for each lipid.

@@

In keeping this previous literature, \cite{Mohwald1990,Vaknin1991}, the tail layer thickness, $d_t$, increases with the number of hydrocarbon atoms present.
Furthermore, the thickness of the tail layers agrees well with values found for water-analogues; \input{../output/dmpc/tail30.txt}\si{\angstrom} at \SI{30}{\milli\newton\per\meter} in DES compared with $d_t=\SI{15.8}{\angstrom}$ at \SI{30}{\milli\newton\per\meter}\cite{Johnson1991} in water for DMPC, and \input{../output/dppc/tail30.txt}\si{\angstrom} at \SI{30}{\milli\newton\per\meter} in DES compared with $d_t=\SI{16.7}{\angstrom}$ at \SI{40}{\milli\newton\per\meter}\cite{Helm1987} in water for DPPC.
In all cases the surface roughness was found to be relatively high when compared to water. However this should be considered in the context that the absolute surface tension of the DES is less than water with a corresponding higher surface roughness\cite{Arnold2015}.

@@

In Figure \ref{fig:lipresults}, it is clear that for all four lipids, as the surface pressure is increased there is a corresponding decrease in the percentage solvent, $\phi_h$, present in the lipid head layer.
This can be rationalised by considering when the surface pressure is increased, the free volume available between the lipid heads reduces forcing the solvent out of the lipid head layer and into the bulk.
A similar effect has been observed when increasing the surface pressure from \SI{11}{\milli\newton\per\meter} to \SI{31}{\milli\newton\per\meter} for a DMPC/DMPG monolayer at the air-water interface\cite{Bayerl1990}.

>>>>

The custom model for each lipid, based on the standard two-layer model widely used for lipids on water, was first fitted to the experimental XRR data, and the associated SLD profiles are shown in Figure \ref{fig:lipids}.
Table \ref{tab:liptab} presents the mean value, and asymmetric uncertainies that correspond to a \SI{95}{\percent} confidence interval, for the PDF for each of the varying parameters; the tail tilt angle, $\theta_t$, the interfacial roughness, $\sigma$, the head and tail volumes, $V_h$ and $V_t$ respectively, and the head layer thickness, $d_h$.
In order to constrain the fitting process only $\theta_t$ and $\sigma$ were allowed to vary independently of surface pressure. The other parameters, $V_h$, $V_t$ and $d_h$ were fitted to a single value for all of the surface pressures measured for each lipid.

@@

In keeping with this previous literature, \cite{Mohwald1990,Vaknin1991}, the tail layer thickness, $d_t$, increases with the number of hydrocarbon atoms present.
Furthermore, the thickness of the tail layers agrees well with values found for water-analogues; \input{../output/dmpc/tail30.txt}\si{\angstrom} at \SI{30}{\milli\newton\per\meter} in DES compared with $d_t=\SI{15.8}{\angstrom}$ at \SI{30}{\milli\newton\per\meter}\cite{Johnson1991} in water for DMPC, and \input{../output/dppc/tail30.txt}\si{\angstrom} at \SI{30}{\milli\newton\per\meter} in DES compared with $d_t=\SI{16.7}{\angstrom}$ at \SI{40}{\milli\newton\per\meter}\cite{Helm1987} in water for DPPC.
In all cases the surface roughness was found to be higher than in water. However this should be considered in the context that the absolute surface tension of the DES is less than water with a corresponding higher surface roughness\cite{Arnold2015}.

@@

In Figure \ref{fig:lipresults}, it is clear that for all four lipids, as the surface pressure is increased there is a corresponding decrease in the percentage solvent, $\phi_h$, present in the lipid head layer.
This can be rationalised by considering when the surface pressure is increased, the free volume available between the lipid heads reduces, forcing the solvent out of the lipid head layer and into the bulk.
A similar effect has been observed when increasing the surface pressure from \SI{11}{\milli\newton\per\meter} to \SI{31}{\milli\newton\per\meter} for a DMPC/DMPG monolayer at the air-water interface\cite{Bayerl1990}.
